---
title: "Market Indicators Lite"
author: "Paul Adamson"
date: "September 11, 2016"
runtime: shiny
output: html_document
---

```{r setup, echo=FALSE}
require(quantmod)
require(stringr)
require(XML)
require(lubridate)
require(xts)
options("getSymbols.warning4.0"=FALSE)
source("./helpers.R")
thm<-chartTheme('white')
thm$bg.col<-'white'
```
[As described by Nellie S. Huang at 
Kiplinger](http://www.kiplinger.com/slideshow/investing/T052-S001-6-key-stock-market-indicators-to-watch-slide-show/index.html#VEQZcU4oQ5l0MEIz.99), 
six key indicators can be used to guage potential for future market gains:

1. S&P 500 Price Versus the 200-Day Moving Average
2. Consumer Confidence
3. Weekly Unemployed Insurance Claims
4. Strength of U.S. Dollar
5. Emerging Markets
6. Price to Earnings Ratio of S&P 500

Due to limitations of free hosting of shiny apps, we will only illustrate the 
first, S&P 500 Price Versus the 200-Day Moving Average.

S&P 500 Price Versus the 200-Day Moving Average
-----------------------------------------------
To compute the 200-Day Moving Average of a stock or market index for a given date, 
one takes the average of the closing prices is defined as the average of daily closing prices  of Standard & Poor's 500-stock index over a 
period of time.

*WHY IT MATTERS*: Many analysts draw the dividing line between bear and bull markets by looking 
at the moving average. If the S&P 500 is trading above its moving average, the thinking goes, 
it's a bull market -- time to invest. If it moves below the average, it's a bear market.

## Usage

The user can easily choose whether to plot the log of price and/or adjust 
for inflation. Also, a slider is provided to easily adjust the timeframe over which
the plot is made.

```{r SPY, echo=FALSE}
minDate=seq(Sys.Date(), length = 2, by = "-10 years")[2]
datesMin=seq(Sys.Date(), length = 2, by = "-12 months")[2]
maxDate=Sys.Date()

fluidPage(
  fluidRow(
    column(3,
           checkboxInput("log", "Y-axis log scale", 
                         value = FALSE)
    ),
    column(3,
           checkboxInput("adjust", 
                         "Adjust for inflation", value = FALSE)
    )
  ),
  fluidRow(
    column(12,
           sliderInput("dates",
                       "Date range",
                       min=minDate,
                       max=maxDate,
                       value=c(datesMin,
                               maxDate),
                       width = "1200px" )
    )
  )
)

spyData <- reactive({
  getSymbols("^GSPC", src = "yahoo", 
             from = input$dates[1],
             to = input$dates[2],
             auto.assign = FALSE,
             method='curl')
})

spyDataAdj <- reactive({
  if (!input$adjust) {
    return(spyData())
  } else {
    return(adjust(spyData()))
  }
})

renderPlot({
  chartSeries(spyDataAdj(), 
              theme = thm, 
              type = "line", 
              log.scale = input$log, 
              TA = NULL,
              name="S&P 500")
  addSMA(n = 200, on = 1, with.col = Cl, overlay = TRUE, col = "black")
})
```
